---
title: "Group Project"
author: "Beau Belkowski, Brian Marquardt, Danny Buglak"
date: '2024-02-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cluster)
library(ggplot2)
library(factoextra)
library(corrplot)
```

```{r}
getwd()
#y2021 <- read.csv("2021.csv")
```

```{r}
y2021 <- read.csv("2021.csv")
y2019 <- read.csv("2019.csv")
y2018 <- read.csv("2018.csv")
y2017 <- read.csv("2017.csv")
y2016 <- read.csv("2016.csv")

y2021
y2019
y2018
y2017
y2016
```

```{r}
y2021$G <- as.double(y2021$G)
y2021$GS <- as.double(y2021$GS)
y2021$Age <- as.double(y2021$Age)
#y2021
```

```{r}
y2021$year<- rep('2021', times= nrow(y2021))
y2021.1 <- y2021[,-1]
#y2021.1
y2018$year<- rep('2018', times= nrow(y2018))
y2018.1 <- y2018[,-1]
#y2018.1
y2019$year<- rep('2019', times= nrow(y2019))
y2019.1 <- y2019[,-1]
#y2019.1
y2017$year<- rep('2017', times= nrow(y2017))
y2017.1 <- y2017[,-1]
#y2017.1
y2016$year<- rep('2016', times= nrow(y2016))
y2016.1 <- y2016[,-1]
#y2016.1


fb <- rbind(y2021.1, y2019.1, y2018.1, y2017.1, y2016.1)
#fb
```
```{r}
fb$Tgt_gm <- fb$Tgt/fb$G
fb$Rec_gm <- fb$Rec/fb$G
fb$PassingYds_gm <- fb$PassingYds/fb$G
fb$PassingTD_gm <- fb$PassingTD/fb$G
fb$PassingAtt_gm <- fb$PassingAtt/fb$G
fb$RushingYds_gm <- fb$RushingYds/fb$G
fb$RushingTD_gm <- fb$RushingTD/fb$G
fb$RushingAtt_gm <- fb$RushingAtt/fb$G
fb$ReceivingYds_gm <- fb$ReceivingYds/fb$G
fb$ReceivingTD_gm <- fb$ReceivingTD/fb$G
fb$FantasyPoints_gm <- fb$FantasyPoints/fb$G
fb$Int_gm <- fb$Int/fb$G
fb$Fumbles_gm <- fb$Fumbles/fb$G
fb$FumblesLost_gm <- fb$FumblesLost/fb$G
summary(fb)
```

```{r}
fb1 <- fb %>%
  filter(GS >= 5, FantasyPoints_gm > 0)
fb1
```


```{r}
rb <- fb1 %>%
  filter(Pos == "RB")
qb <- fb1 %>%
  filter(Pos == "QB")
wr <- fb1 %>%
  filter(Pos == "WR")
te <- fb1 %>%
  filter(Pos == "TE")
rb
qb
wr
te
```

```{r}

ggplot(data = fb1, aes(x = FantasyPoints_gm)) + 
  geom_histogram() +
  ggtitle("Distribution of Fantasy Points per Game")

ggplot(data = rb, aes(x = RushingYds_gm)) + 
  geom_histogram() +
  ggtitle("Distribution of Runningbacks Rushing Yards per Game")

ggplot(data = qb, aes(x = PassingTD_gm)) + 
  geom_histogram() +
  ggtitle("Distribution of Quarterbacks Passing Touchdowns per Game")

ggplot(data = rb, aes(x = FantasyPoints_gm, y = RushingYds_gm)) + 
  geom_point() +
  ggtitle("Correlation for Running Backs Fantasy Points per Game and Rushing Yards per Game")

ggplot(data = fb1, aes(x = FantasyPoints_gm, y = FumblesLost_gm)) + 
  geom_point() +
  ggtitle("Correlation Between Fantasy Points per Game and Fumbles Lost per Game")

ggplot(data = wr, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point() +
  ggtitle("Correlation for Wide Recievers Fantasy Points per Game and Recieving Touchdowns per Game")
```
```{r}
rb1 <- rb %>%
  filter(RushingYds_gm == 0)
rb1
```

```{r}
qb_gm <- qb %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

rb_gm <- rb %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

wr_gm <- wr %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

te_gm <- te %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)
```


```{r}

qbcorr <- subset(qb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(qbcorr), method ="circle")

rbcorr <- subset(rb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(rbcorr), method ="circle")

wrcorr <- subset(wr_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(wrcorr), method ="circle")

tecorr <- subset(te_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(tecorr), method ="circle")
```
```{r}
# Most highly correlated stats with qb success
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingTD_gm)
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingYds_gm)
cor(qb_gm$FantasyPoints_gm, qb_gm$GS)
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingAtt_gm)
```

```{r}
ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```


```{r}
# Most highly correlated stats with rb success
cor(rb_gm$FantasyPoints_gm, rb_gm$Tgt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$Rec_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingAtt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$GS)
```

```{r}
ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
# Most highly correlated stats with wr success
cor(wr_gm$FantasyPoints_gm, wr_gm$GS)
cor(wr_gm$FantasyPoints_gm, wr_gm$Tgt_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$Rec_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingTD_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingYds_gm)
```

```{r}
ggplot(wr_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
# Most highly correlated stats with te success
cor(te_gm$FantasyPoints_gm, te_gm$Tgt_gm)
cor(te_gm$FantasyPoints_gm, te_gm$Rec_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingTD_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingYds_gm)
```

```{r}
ggplot(te_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```









## Clustering Analysis

```{r}
set.seed(20)

# Remove name and team and omit any NA values
clust_fb <- fb1 %>% 
  select(-c("Player", "Tm")) %>%
  na.omit()

# Scale the data to normalize it
normalized_fb <- scale(clust_fb[, sapply(clust_fb, is.numeric)])

# Determine the optimal number of clusters using Elbow method
elbow <- sapply(1:15, function(k) {
  kmeans(normalized_fb, centers = k, nstart = 50)$tot.withinss
  })
plot(1:15, elbow, type="b", xlab="Number of Clusters", ylab="Within groups sum of squares")
```

Elbow Method shows that 4 is the optimal number of clusters. This is because 4 is when the line on the graph "elbows", or where it begins to shallow out and adding any more clusters than 4 do not change the analysis by much.

```{r cluster-creation}
set.seed(20)

# Performs k means on normalized data set
k <- kmeans(normalized_fb, centers = 4)

# Add cluster information to original data set
clust_fb$cluster <- k$cluster

# For factor or character variables, use table to get counts for each cluster
position_counts <- table(clust_fb$cluster, clust_fb$Pos)

get_mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

# Apply the custom mode function to get the most common position per cluster
common_positions <- tapply(clust_fb$Pos, clust_fb$cluster, get_mode)
common_positions



```

After performing kmeans on the normalized data set, we can see how the clusters were created. The clusters correspond as follows:

1: QB (Quarter Back)

2: TE (Tight End)

3: RB (Running Back)

4: WR (Wide Receiver)


```{r}
# First, create a data frame with only numeric columns and cluster assignment
numeric_columns <- clust_fb %>% select(cluster, where(is.numeric))

# Aggregate the results to view the cluster summary
cluster_summary <- aggregate(. ~ cluster, data=numeric_columns, mean)
cluster_summary
```

Then, we can aggregate the data to show the averages for each position. For example, the average age for a tight end in 26.4 with an average 8.26 games started. There are some dissimilar properties for each cluster, for example the QB average passing touchdowns are much higher than the other three positions, but this is as expected due to the position.

```{r tables}
# Format a table relating Games Started and cluster
gs_table <- table(clust_fb$cluster, clust_fb$GS)
gs_prop <- prop.table(gs_table, margin=1) * 100
gs_prop_formatted <- apply(gs_prop, c(1, 2), function(x) paste0(round(x, 1), "%"))
data.frame(gs_prop_formatted)


#fp_table <- table(clust_fb$cluster, clust_fb$FantasyPoints)
#fp_prop <- prop.table(fp_table, margin=1) * 100
#fp_prop_formatted <- apply(fp_prop, c(1, 2), function(x) paste0(round(x, 1), "%"))
#fp_prop_formatted

#fpG_table <- table(clust_fb$cluster, clust_fb$FantasyPoints_gm)
#fpG_prop <- prop.table(fpG_table, margin=1) * 100
#fpG_prop_formatted <- apply(fpG_prop, c(1, 2), function(x) paste0(round(x, 1), "%"))
#fpG_prop_formatted
```

Next, we can format tables to show different statistics that are common in each cluster. The gs_table data frame shows that, on average, most quarter backs start 16 games. Most tight ends start 5 games, on average. Most running backs start 16 games on average. Finally, wide receivers start 16 games on average. These are calculate from finding the proportion of games started for each position and put into a data frame. Then, the highest value in each row is the largest proportion of games started for the respective position.

```{r cluster-visualization}

# Cluster visualization with Games Started vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints", "GS")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
  labs(x = "Fantasy Points", y = "Games Started")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints, y = GS, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "Games Started", color = "Cluster") +
  theme_minimal()

```

Using GGplot and Factoextra to visualize the kmeans for Fantasy Points vs. Games started, you can see that the more games started correlates to more fantasy points. There are a few outliers, for example, one point is at approximately 8 games started with 300+ fantasy points. But the grey dots and circle have the majority of the high fantasy points in the league.

```{r cluster-visualization2}

# Cluster visualization with Targets vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints", "Tgt")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
  labs(x = "Fantasy Points", y = "Targets")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints, y = Tgt, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "Targets", color = "Cluster") +
  theme_minimal()

```


The bottom two show that fumbles and fumbles lost do not have a big correlation with the amount of fantasy points

```{r cluster-visualization3}

# Cluster visualization with Fumbles vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints", "Fumbles")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
  labs(x = "Fantasy Points", y = "Fumbles")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints, y = Fumbles, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "Fumbles", color = "Cluster") +
  theme_minimal()

```

The above plots and output show that the amount of fumbles does not necessarily affect how many fantasy points each position received.


```{r cluster-visualization4}

# Cluster visualization with Fumbles Lost vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints", "FumblesLost")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
  labs(x = "Fantasy Points", y = "FumblesLost")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints, y = FumblesLost, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "FumblesLost", color = "Cluster") +
  theme_minimal()

```

```{r cluster-visualization5}

# Cluster visualization with Fumbles Lost vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "FumblesLost_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
  labs(x = "Fantasy Points", y = "FumblesLost_gm")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = FumblesLost_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "FumblesLost_gm", color = "Cluster") +
  theme_minimal()

```

```{r cluster-visualization6}

# Cluster visualization with Fumbles Lost vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "Fumbles_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
  labs(x = "Fantasy Points", y = "Fumbles_gm")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = Fumbles_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "Fumbles_gm", color = "Cluster") +
  theme_minimal()

```

These two show the Fantasy points per game and fumbles lost and fumbles per game (respectively). This also shows that the amount of fumbles does not necessarily mean a lower fantasy points per game.




```{r boxplots}
# ALL X AXIS ARE THE CLUSTER

# RECEIVING YARDS PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=ReceivingYds_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Receiving Yards per Game")

# GAMES STARTED 
ggplot(clust_fb, aes(x=factor(cluster), y=GS, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Games Started")

# PASSING YARDS PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=PassingYds_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Passing Yards per Game")

# FANTASY POINTS PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=FantasyPoints_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fantasy Points per Game")

# TOTAL FANTASY POINTS
ggplot(clust_fb, aes(x=factor(cluster), y=FantasyPoints, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fantasy Points")

# FUMBLES PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=Fumbles_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fumbles per Game")

# FUMBLES LOST PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=FumblesLost_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fumbles Lost per Game")
```


