---
title: "Group Project"
author: "Beau Belkowski, Brian Marquardt, Danny Buglak"
date: "2024-02-27"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(cluster)
library(ggplot2)
library(factoextra)
library(corrplot)
```

```{r}
getwd()
```

```{r}
y2021 <- read.csv("2021.csv")
y2019 <- read.csv("2019.csv")
y2018 <- read.csv("2018.csv")
y2017 <- read.csv("2017.csv")
y2016 <- read.csv("2016.csv")

y2021
y2019
y2018
y2017
y2016
```

```{r}
y2021$G <- as.double(y2021$G)
y2021$GS <- as.double(y2021$GS)
y2021$Age <- as.double(y2021$Age)
#y2021
```

```{r}
y2021$year<- rep('2021', times= nrow(y2021))
y2021.1 <- y2021[,-1]
#y2021.1
y2018$year<- rep('2018', times= nrow(y2018))
y2018.1 <- y2018[,-1]
#y2018.1
y2019$year<- rep('2019', times= nrow(y2019))
y2019.1 <- y2019[,-1]
#y2019.1
y2017$year<- rep('2017', times= nrow(y2017))
y2017.1 <- y2017[,-1]
#y2017.1
y2016$year<- rep('2016', times= nrow(y2016))
y2016.1 <- y2016[,-1]
#y2016.1


fb <- rbind(y2021.1, y2019.1, y2018.1, y2017.1, y2016.1)
#fb
```
```{r}
fb$Tgt_gm <- fb$Tgt/fb$G
fb$Rec_gm <- fb$Rec/fb$G
fb$PassingYds_gm <- fb$PassingYds/fb$G
fb$PassingTD_gm <- fb$PassingTD/fb$G
fb$PassingAtt_gm <- fb$PassingAtt/fb$G
fb$RushingYds_gm <- fb$RushingYds/fb$G
fb$RushingTD_gm <- fb$RushingTD/fb$G
fb$RushingAtt_gm <- fb$RushingAtt/fb$G
fb$ReceivingYds_gm <- fb$ReceivingYds/fb$G
fb$ReceivingTD_gm <- fb$ReceivingTD/fb$G
fb$FantasyPoints_gm <- fb$FantasyPoints/fb$G
fb$Int_gm <- fb$Int/fb$G
fb$Fumbles_gm <- fb$Fumbles/fb$G
fb$FumblesLost_gm <- fb$FumblesLost/fb$G
summary(fb)
```

```{r}
fb1 <- fb %>%
  filter(GS >= 5, FantasyPoints_gm > 0)
fb1
```


```{r}
rb <- fb1 %>%
  filter(Pos == "RB")
qb <- fb1 %>%
  filter(Pos == "QB")
wr <- fb1 %>%
  filter(Pos == "WR")
te <- fb1 %>%
  filter(Pos == "TE")
rb
qb
wr
te
```

```{r}

ggplot(data = fb1, aes(x = FantasyPoints_gm)) + 
  geom_histogram(color = "black", fill = "white") +
  ggtitle("Distribution of Fantasy Points per Game")+
  xlab("Fantasy Pointer per Game for all players")

ggplot(data = rb, aes(x = RushingYds_gm)) + 
  geom_histogram(color = "black", fill = "white") +
  ggtitle("Distribution of Running Backs Rushing Yards per Game")+
  xlab("Rushing Yards per Game")

ggplot(data = qb, aes(x = PassingTD_gm)) + 
  geom_histogram(color = "black", fill = "white") +
  ggtitle("Distribution of Quarterbacks Passing Touchdowns per Game")+
  xlab("Passing Touchdowns per Game")

ggplot(data = rb, aes(x = FantasyPoints_gm, y = RushingYds_gm)) + 
  geom_point() +
  ggtitle("Correlation for Running Backs Fantasy Points per Game and 
          \n Rushing Yards per Game")+
  xlab("Fantasy Points per Game")+
  ylab("Rushing Yards per Game")

ggplot(data = fb1, aes(x = FantasyPoints_gm, y = FumblesLost_gm)) + 
  geom_point() +
  ggtitle("Correlation Between Fantasy Points per Game and \n Fumbles Lost per 
          Game")+
  xlab("Fantasy Points per Game")+
  ylab("Fumbles Lost per Game")

ggplot(data = wr, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point() +
  ggtitle("Correlation for Wide Recievers Fantasy Points per Game and \n 
          Recieving Touchdowns per Game")+
  xlab("Fantasy Points per Game")+
  ylab("Recieving Touchdowns per Game")
```
```{r}
rb1 <- rb %>%
  filter(RushingYds_gm == 0)
rb1
```

```{r}
library(tidyverse)
qb_gm <- qb %>% dplyr::select(Player, Tm, Pos, Age, G, GS, year, Tgt_gm, 
                              Rec_gm, PassingYds_gm, PassingTD_gm, 
                              PassingAtt_gm, RushingYds_gm, RushingTD_gm, 
                              RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, 
                              FantasyPoints_gm, Int_gm, Fumbles_gm, 
                              FumblesLost_gm)

rb_gm <- rb %>% dplyr::select(Player, Tm, Pos, Age, G, GS, year, Tgt_gm, 
                              Rec_gm, PassingYds_gm, PassingTD_gm, 
                              PassingAtt_gm, RushingYds_gm, RushingTD_gm, 
                              RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, 
                              FantasyPoints_gm, Int_gm, Fumbles_gm, 
                              FumblesLost_gm)

wr_gm <- wr %>% dplyr::select(Player, Tm, Pos, Age, G, GS, year, Tgt_gm, 
                              Rec_gm, PassingYds_gm, PassingTD_gm, 
                              PassingAtt_gm, RushingYds_gm, RushingTD_gm, 
                              RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, 
                              FantasyPoints_gm, Int_gm, Fumbles_gm, 
                              FumblesLost_gm)

te_gm <- te %>% dplyr::select(Player, Tm, Pos, Age, G, GS, year, Tgt_gm, 
                              Rec_gm, PassingYds_gm, PassingTD_gm, 
                              PassingAtt_gm, RushingYds_gm, RushingTD_gm, 
                              RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, 
                              FantasyPoints_gm, Int_gm, Fumbles_gm, 
                              FumblesLost_gm)
```


```{r}

qbcorr <- subset(qb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(qbcorr), method ="circle")

rbcorr <- subset(rb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(rbcorr), method ="circle")

wrcorr <- subset(wr_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(wrcorr), method ="circle")

tecorr <- subset(te_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(tecorr), method ="circle")
```
```{r}
# Most highly correlated stats with qb success
cor(qb_gm$FantasyPoints_gm, qb$PassingTD_gm)
cor(qb_gm$FantasyPoints_gm, qb$PassingYds_gm)
cor(qb_gm$FantasyPoints_gm, qb$GS)
cor(qb_gm$FantasyPoints_gm, qb$PassingAtt_gm)
```

```{r}
ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Passing Touchdowns per Game and Fantasy Points 
          per Game")+
  xlab("Fantasy Points per Game")+
  ylab("Passing Touchdowns per Game")

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Passing Yards per Game and Fantasy Points per 
          Game")+
  xlab("Fantasy Points per Game")+
  ylab("Passing Yards per Game")

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```


```{r}
# Most highly correlated stats with rb success
cor(rb_gm$FantasyPoints_gm, rb_gm$Tgt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$Rec_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingAtt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$GS)
```

```{r}
ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Rushing Yards per Game and Fantasy Points 
          per Game")+
  xlab("Fantasy Points per Game")+
  ylab("Rushing Yards per Game")

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Recieving Touchdowns per Game and Fantasy Points
          per Game")+
  xlab("Fantasy Points per Game")+
  ylab("Recieving Touchdowns per Game")

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
# Most highly correlated stats with wr success
cor(wr_gm$FantasyPoints_gm, wr_gm$GS)
cor(wr_gm$FantasyPoints_gm, wr_gm$Tgt_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$Rec_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingTD_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingYds_gm)
```

```{r}
ggplot(wr_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Games Started and Fantasy Points per Game")+
  xlab("Fantasy Points per Game")+
  ylab("Games Started")

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Recieving Yards per Game and Fantasy Points per 
          Game")+
  xlab("Fantasy Points per Game")+
  ylab("Recieving Yards per Game")
```

```{r}
# Most highly correlated stats with te success
cor(te_gm$FantasyPoints_gm, te_gm$Tgt_gm)
cor(te_gm$FantasyPoints_gm, te_gm$Rec_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingTD_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingYds_gm)
```

```{r}
ggplot(te_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Recieving Touchdowns per Game and Fantasy Points
          per \n Game")+
  xlab("Fantasy Points per Game")+
  ylab("Recieving Touchdowns per Game")

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)+
  ggtitle("Correlation Between Recieving Yards per Game and Fantasy Points per 
          Game")+
  xlab("Fantasy Points per Game")+
  ylab("Recieving Yards per Game")
```









## Clustering Analysis

```{r elbow-method}
set.seed(20)

# Remove name and team and omit any NA values
clust_fb <- fb1 %>% 
  select(-c("Player", "Tm")) %>%
  na.omit()

# Scale the data to normalize it
normalized_fb <- scale(clust_fb[, sapply(clust_fb, is.numeric)])

# Determine the optimal number of clusters using Elbow method
elbow <- sapply(1:15, function(k) {
  kmeans(normalized_fb, centers = k, nstart = 50)$tot.withinss
  })
plot(1:15, elbow, type="b", xlab="Number of Clusters", ylab="Within groups sum of squares")
```

Elbow Method shows that 4 is the optimal number of clusters. This is because 4 is when the line on the graph "elbows", or where it begins to shallow out and adding any more clusters than 4 do not change the analysis by much.

```{r cluster-creation}
set.seed(20)

# Performs k means on normalized data set
k <- kmeans(normalized_fb, centers = 4)

# Add cluster information to original data set
clust_fb$cluster <- k$cluster

# For factor or character variables, use table to get counts for each cluster
position_counts <- table(clust_fb$cluster, clust_fb$Pos)

get_mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

# Apply the custom mode function to get the most common position per cluster
common_positions <- tapply(clust_fb$Pos, clust_fb$cluster, get_mode)
common_positions



```

After performing kmeans on the normalized data set, we can see how the clusters were created. The clusters correspond as follows:

1: QB (Quarter Back)

2: TE (Tight End)

3: RB (Running Back)

4: WR (Wide Receiver)


```{r}
# First, create a data frame with only numeric columns and cluster assignment
numeric_columns <- clust_fb %>% select(cluster, where(is.numeric))

# Aggregate the results to view the cluster summary
cluster_summary <- aggregate(. ~ cluster, data=numeric_columns, mean)
cluster_summary
```

Then, we can aggregate the data to show the averages for each position. For example, the average age for a tight end in 26.4 with an average 8.26 games started. There are some dissimilar properties for each cluster, for example the QB average passing touchdowns are much higher than the other three positions, but this is as expected due to the position.

```{r tables}
# Format a table relating Games Started and cluster
gs_table <- table(clust_fb$cluster, clust_fb$GS)
gs_prop <- prop.table(gs_table, margin=1) * 100
gs_prop_formatted <- apply(gs_prop, c(1, 2), function(x) paste0(round(x, 1), "%"))
data.frame(gs_prop_formatted)


#fp_table <- table(clust_fb$cluster, clust_fb$FantasyPoints)
#fp_prop <- prop.table(fp_table, margin=1) * 100
#fp_prop_formatted <- apply(fp_prop, c(1, 2), function(x) paste0(round(x, 1), "%"))
#fp_prop_formatted

#fpG_table <- table(clust_fb$cluster, clust_fb$FantasyPoints_gm)
#fpG_prop <- prop.table(fpG_table, margin=1) * 100
#fpG_prop_formatted <- apply(fpG_prop, c(1, 2), function(x) paste0(round(x, 1), "%"))
#fpG_prop_formatted
```

Next, we can format tables to show different statistics that are common in each cluster. The gs_table data frame shows that, on average, most quarter backs start 16 games. Most tight ends start 5 games, on average. Most running backs start 16 games on average. Finally, wide receivers start 16 games on average. These are calculate from finding the proportion of games started for each position and put into a data frame. Then, the highest value in each row is the largest proportion of games started for the respective position.

```{r cluster-visualization}

# Cluster visualization with Games Started vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints", "GS")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points", y = "Games Started") +
  ggtitle("Fantasy Points vs. Games Started")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints, y = GS, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "Games Started", color = "Cluster") +
  theme_minimal()

```

Using GGplot and Factoextra to visualize the kmeans for Fantasy Points vs. Games started, you can see that the more games started correlates to more fantasy points. There are a few outliers, for example, one point is at approximately 8 games started with 300+ fantasy points. But the grey dots and circle have the majority of the high fantasy points in the league.

```{r cluster-visualization2}

# Cluster visualization with Targets vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "Tgt_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points per Game", y = "Targets per Game") +
  ggtitle("Fantasy Points per Game vs Targets per Game")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = Tgt_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points per Game", y = "Targets per Game", color = "Cluster") +
  theme_minimal()

```

```{r cluster-visualization2-2}

# Cluster visualization with Targets vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "Rec_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points per Game", y = "Receptions per Game") +
  ggtitle("Fantasy Points per Game vs Receptions per Game")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = Rec_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points per Game", y = "Receptions per Game", color = "Cluster") +
  theme_minimal()

```

The bottom two show that fumbles and fumbles lost do not have a big correlation with the amount of fantasy points

```{r cluster-visualization3}

# Cluster visualization with Fumbles vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints", "Fumbles")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points", y = "Fumbles")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints, y = Fumbles, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "Fumbles", color = "Cluster") +
  theme_minimal()

```

The above plots and output show that the amount of fumbles does not necessarily affect how many fantasy points each position received.


```{r cluster-visualization4}

# Cluster visualization with Fumbles Lost vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints", "FumblesLost")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points", y = "Fumbles Lost") +
            ggtitle("Fantasy Points vs Fumbles Lost") 

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints, y = FumblesLost, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points", y = "Fumbles Lost", color = "Cluster") +
  ggtitle("Fantasy Points vs Fumbles Lost") + 
  theme_minimal()

```

```{r cluster-visualization5}

# Cluster visualization with Fumbles Lost vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "FumblesLost_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points per Game", y = "FumblesLost per Game") +
             ggtitle("Fantasy Points per Game vs Fumbles Lost per Game")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = FumblesLost_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points per Game", y = "Fumbles Lost per Game", color = "Cluster") +
  ggtitle("Fantasy Points per Game vs Fumbles Lost per Game") + 
  theme_minimal()

```

```{r cluster-visualization6}

# Cluster visualization with Fumbles Lost vs FantasyPoints

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "Fumbles_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points per game", y = "Fumbles per Game")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = Fumbles_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points per Game", y = "Fumbles per Game", color = "Cluster") +
  theme_minimal()

```

These two show the Fantasy points per game and fumbles lost and fumbles per game (respectively). This also shows that the amount of fumbles does not necessarily mean a lower fantasy points per game.

```{r cluster-visualization7}

# Cluster visualization with Receiving TDs per game vs FantasyPoints per game

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "ReceivingTD_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points", y = "Receiving Touchdowns per Game") +
  ggtitle("Fantasy Points vs. Receiving Touchdowns per Game")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = ReceivingTD_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points per Game", y = "Receiving Touchdowns per Game", color = "Cluster") +
  theme_minimal()

```

```{r cluster-visualization8}

# Cluster visualization with Rushing TDs per game vs FantasyPoints per game

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "RushingTD_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points", y = "Rushing Touchdowns per Game") +
  ggtitle("Fantasy Points vs. Rushing Touchdowns per Game")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = RushingTD_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points per Game", y = "Rushing Touchdowns per Game", color = "Cluster") +
  theme_minimal()

```

```{r cluster-visualization9}

# Cluster visualization with Passing TDs per game vs FantasyPoints per game

# Extract just the FantasyPoints and GS columns for k-means
fb_subset <- clust_fb[, c("FantasyPoints_gm", "PassingTD_gm")]

summary(fb_subset)

# Perform k-means
set.seed(20)
k_fb_subset <- kmeans(fb_subset, centers = 4)  
k_fb_subset$centers

# Create a data frame with the results
fb_clustered <- data.frame(fb_subset, cluster = factor(k_fb_subset$cluster))

# fviz_cluster to visualize normalized data
fviz_cluster(object = list(data = fb_subset, cluster = k_fb_subset$cluster), 
             palette = "jco", 
             ggtheme = theme_minimal()) +
             labs(x = "Fantasy Points", y = "Passing Touchdowns per Game") +
  ggtitle("Fantasy Points vs. Passing Touchdowns per Game")

# GGplot to visualize
ggplot(fb_clustered, aes(x = FantasyPoints_gm, y = PassingTD_gm, color = cluster)) +
  geom_point() +
  scale_color_manual(values = c("cadetblue", "yellow3", "cornsilk3", "brown1")) +
  labs(x = "Fantasy Points per Game", y = "Rushing Touchdowns per Game", color = "Cluster") +
  theme_minimal()

```

```{r cluster-visualization10}

# QB CLUSTERING ANALYSIS

# Prepare QB data subsets for clustering
qb_data_features <- qb %>% 
  select(FantasyPoints_gm, Int_gm, PassingTD_gm, PassingYds_gm, PassingAtt_gm)

# Clustering for each feature pair
set.seed(20)
k_qb_int <- kmeans(qb_data_features[, c("FantasyPoints_gm", "Int_gm")], centers = 4)
k_qb_int$centers
k_qb_td <- kmeans(qb_data_features[, c("FantasyPoints_gm", "PassingTD_gm")], centers = 4)
k_qb_td$centers
k_qb_yds <- kmeans(qb_data_features[, c("FantasyPoints_gm", "PassingYds_gm")], centers = 4)
k_qb_yds$centers
k_qb_att <- kmeans(qb_data_features[, c("FantasyPoints_gm", "PassingAtt_gm")], centers = 4)
k_qb_att$centers

# Interceptions vs. Fantasy Points
fviz_cluster(list(data = qb_data_features[, c("FantasyPoints_gm", "Int_gm")], cluster = k_qb_int$cluster), 
             palette = "jco",
             ggtheme = theme_minimal()) +
  labs(title = "Interceptions vs. Fantasy Points", 
       x = "Fantasy Points per Game", y = "Interceptions per Game")

# Passing Yards vs. Fantasy Points
fviz_cluster(list(data = qb_data_features[, c("FantasyPoints_gm", "PassingTD_gm")], cluster = k_qb_int$cluster), 
             palette = "jco",
             ggtheme = theme_minimal()) +
  labs(title = "Passing Touchdowns per Game vs. Fantasy Points", 
       x = "Fantasy Points per Game", y = "Passing Touchdowns per Game")

# Passing Touchdowns vs. Fantasy Points
fviz_cluster(list(data = qb_data_features[, c("FantasyPoints_gm", "PassingYds_gm")], cluster = k_qb_int$cluster), 
             palette = "jco",
             ggtheme = theme_minimal()) +
  labs(title = "Passing Yards per Game vs. Fantasy Points", 
       x = "Fantasy Points per Game", y = "Passing Yards per Game")

# Passing Attempts vs. Fantasy Points
fviz_cluster(list(data = qb_data_features[, c("FantasyPoints_gm", "PassingAtt_gm")], cluster = k_qb_int$cluster), 
             palette = "jco",
             ggtheme = theme_minimal()) +
  labs(title = "Passing Attempts per game vs. Fantasy Points", 
       x = "Fantasy Points per Game", y = "Passing Attempts per Game")


```






```{r boxplots}
# ALL X AXIS ARE THE CLUSTER

# RECEIVING YARDS PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=ReceivingYds_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Receiving Yards per Game")

# GAMES STARTED 
ggplot(clust_fb, aes(x=factor(cluster), y=GS, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Games Started")

# PASSING YARDS PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=PassingYds_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Passing Yards per Game")

# FANTASY POINTS PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=FantasyPoints_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fantasy Points per Game")

# TOTAL FANTASY POINTS
ggplot(clust_fb, aes(x=factor(cluster), y=FantasyPoints, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fantasy Points")

# FUMBLES PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=Fumbles_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fumbles per Game")

# FUMBLES LOST PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=FumblesLost_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Fumbles Lost per Game")

# RUSHING TD PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=RushingTD_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Rushing Touchdowns Per Game")

# RECEIVING TD PER GAME
ggplot(clust_fb, aes(x=factor(cluster), y=ReceivingTD_gm, fill=factor(cluster))) + 
  geom_boxplot() + 
  labs(x="Cluster", y="Receiving Touchdowns Per Game")
```


```{r}

rb1 <- rb %>%
  filter(RushingYds_gm == 0)
rb1
```

```{r}
qb_gm <- qb %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

rb_gm <- rb %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

wr_gm <- wr %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

te_gm <- te %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)
```


```{r}
library(corrplot)

qbcorr <- subset(qb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(qbcorr), method ="circle")

rbcorr <- subset(rb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(rbcorr), method ="circle")

wrcorr <- subset(wr_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(wrcorr), method ="circle")

tecorr <- subset(te_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(tecorr), method ="circle")
```
```{r}
# Most highly correlated stats with qb success
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingTD_gm)
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingYds_gm)
cor(qb_gm$FantasyPoints_gm, qb_gm$GS)
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingAtt_gm)
```

```{r}
ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```


```{r}
# Most highly correlated stats with rb success
cor(rb_gm$FantasyPoints_gm, rb_gm$Tgt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$Rec_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingAtt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$GS)
```

```{r}
ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
# Most highly correlated stats with wr success
cor(wr_gm$FantasyPoints_gm, wr_gm$GS)
cor(wr_gm$FantasyPoints_gm, wr_gm$Tgt_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$Rec_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingTD_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingYds_gm)
```

```{r}
ggplot(wr_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
# Most highly correlated stats with te success
cor(te_gm$FantasyPoints_gm, te_gm$Tgt_gm)
cor(te_gm$FantasyPoints_gm, te_gm$Rec_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingTD_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingYds_gm)
```

```{r}
library(ggplot2)
ggplot(te_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
#QB Linear Models
qb_PassingTD_gm_model <- lm(FantasyPoints_gm ~ PassingTD_gm, data = qb_gm)
qb_PassingYds_gm_model <- lm(FantasyPoints_gm ~ PassingYds_gm, data = qb_gm)
qb_GS_model <- lm(FantasyPoints_gm ~ GS, data = qb_gm)
qb_PassingAtt_gm_model <- lm(FantasyPoints_gm ~ PassingAtt_gm, data = qb_gm)

# Adjusted R squared values
PassingTD_summary <- summary(qb_PassingTD_gm_model)
adjusted_r_squared <- PassingTD_summary$adj.r.squared
adjusted_r_squared

PassingYds_summary <- summary(qb_PassingYds_gm_model)
adjusted_r_squared <- PassingYds_summary$adj.r.squared
adjusted_r_squared

PassingAtt_summary <- summary(qb_PassingAtt_gm_model)
adjusted_r_squared <- PassingAtt_summary$adj.r.squared
adjusted_r_squared

GS_summary <- summary(qb_GS_model)
adjusted_r_squared <- GS_summary$adj.r.squared
adjusted_r_squared


# Combined QB model
all_qb_model <- lm(FantasyPoints_gm ~ PassingTD_gm + PassingYds_gm + PassingAtt_gm + GS, data = qb_gm)
summary(all_qb_model)


```
QB prediction equation
FantasyPoints_gm = 0.361 + 4.335(PassingTD_gm) + 0.034(PassingYds_gm) - 0.031(PassingAtt_gm) + 0.153(GS)


```{r}
# QB Residual Standard Error
qbTD_residuals <- resid(qb_PassingTD_gm_model)
qb_RSE1 <- sqrt(sum(qbTD_residuals^2) / (length(qbTD_residuals) - length(qb_PassingTD_gm_model$coefficients) - 1))

qbYDS_residuals <- resid(qb_PassingYds_gm_model)
qb_RSE2 <- sqrt(sum(qbYDS_residuals^2) / (length(qbYDS_residuals) - length(qb_PassingYds_gm_model$coefficients) - 1))

qbGS_residuals <- resid(qb_GS_model)
qb_RSE3 <- sqrt(sum(qbGS_residuals^2) / (length(qbGS_residuals) - length(qb_GS_model$coefficients) - 1))

qbAtt_residuals <- resid(qb_PassingAtt_gm_model)
qb_RSE4 <- sqrt(sum(qbAtt_residuals^2) / (length(qbAtt_residuals) - length(qb_PassingAtt_gm_model$coefficients) - 1))

qb_variable_names <- c("PassingTD_gm", "PassingYds_gm", "PassingAtt_gm", "GS")
qb_RSE_values <- c(qb_RSE1, qb_RSE2, qb_RSE3, qb_RSE4)
qb_RSE_table <- data.frame(Variable = qb_variable_names, RSE = qb_RSE_values)
print(qb_RSE_table)
```




```{r}
#RB Linear Models
rb_Tgt_gm_model <- lm(FantasyPoints_gm ~ Tgt_gm, data = rb_gm)
rb_Rec_gm_model <- lm(FantasyPoints_gm ~ Rec_gm, data = rb_gm)
rb_RushingYds_gm_model <- lm(FantasyPoints_gm ~ RushingYds_gm, data = rb_gm)
rb_RushingTD_gm_model <- lm(FantasyPoints_gm ~ RushingTD_gm, data = rb_gm)
rb_RushingAtt_gm_model <- lm(FantasyPoints_gm ~ RushingAtt_gm, data = rb_gm)
rb_ReceivingYds_gm_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm, data = rb_gm)
rb_ReceivingTD_gm_model <- lm(FantasyPoints_gm ~ ReceivingTD_gm, data = rb_gm)
rb_GS_model <- lm(FantasyPoints_gm ~ GS, data = rb_gm)


# Adjusted R squared values
RushingYds_gm_summary <- summary(rb_RushingYds_gm_model)
adjusted_r_squared <- RushingYds_gm_summary$adj.r.squared
adjusted_r_squared

RushingAtt_gm_summary <- summary(rb_RushingAtt_gm_model)
adjusted_r_squared <- RushingAtt_gm_summary$adj.r.squared
adjusted_r_squared

Rec_gm_summary <- summary(rb_Rec_gm_model)
adjusted_r_squared <- Rec_gm_summary$adj.r.squared
adjusted_r_squared

Tgt_gm_summary <- summary(rb_Tgt_gm_model)
adjusted_r_squared <- Tgt_gm_summary$adj.r.squared
adjusted_r_squared

ReceivingYds_gm_summary <- summary(rb_ReceivingYds_gm_model)
adjusted_r_squared <- ReceivingYds_gm_summary$adj.r.squared
adjusted_r_squared

RushingTD_gm_summary <- summary(rb_RushingTD_gm_model)
adjusted_r_squared <- RushingTD_gm_summary$adj.r.squared
adjusted_r_squared

GS_summary <- summary(rb_GS_model)
adjusted_r_squared <- GS_summary$adj.r.squared
adjusted_r_squared

ReceivingTD_gm_summary <- summary(rb_ReceivingTD_gm_model)
adjusted_r_squared <- ReceivingTD_gm_summary$adj.r.squared
adjusted_r_squared

# Combined RB model
all_rb_model <- lm(FantasyPoints_gm ~ Tgt_gm + Rec_gm + RushingYds_gm + RushingTD_gm + RushingAtt_gm + ReceivingYds_gm + ReceivingTD_gm + GS, data = rb_gm)
summary(all_rb_model)

```
RB prediction equation
FantasyPoints_gm = -0.059 + 0.286(Tgt_gm) + 0.347(Rec_gm) - 0.101(RushingYds_gm) + 5.972(RushingTD_gm) - 0.018(RushingAtt_gm) + 0.115(ReceivingYds_gm) + 6.253(ReceivingTD_gm) - 0.005(GS)

```{r}
# RB Residual Standard Error
rbRushYds_residuals <- resid(rb_RushingYds_gm_model)
rb_RSE1 <- sqrt(sum(rbRushYds_residuals^2) / (length(rbRushYds_residuals) - length(rb_RushingYds_gm_model$coefficients) - 1))

rbRushAtt_residuals <- resid(rb_RushingAtt_gm_model)
rb_RSE2 <- sqrt(sum(rbRushAtt_residuals^2) / (length(rbRushAtt_residuals) - length(rb_RushingAtt_gm_model$coefficients) - 1))

rbRec_residuals <- resid(rb_Rec_gm_model)
rb_RSE3 <- sqrt(sum(rbRec_residuals^2) / (length(rbRec_residuals) - length(rb_Rec_gm_model$coefficients) - 1))

rbTgt_residuals <- resid(rb_Tgt_gm_model)
rb_RSE4 <- sqrt(sum(rbTgt_residuals^2) / (length(rbTgt_residuals) - length(rb_Tgt_gm_model$coefficients) - 1))

rbRecYds_residuals <- resid(rb_ReceivingYds_gm_model)
rb_RSE5 <- sqrt(sum(rbRecYds_residuals^2) / (length(rbRecYds_residuals) - length(rb_ReceivingYds_gm_model$coefficients) - 1))

rbRushTD_residuals <- resid(rb_RushingTD_gm_model)
rb_RSE6 <- sqrt(sum(rbRushTD_residuals^2) / (length(rbRushTD_residuals) - length(rb_RushingTD_gm_model$coefficients) - 1))

rbGS_residuals <- resid(rb_GS_model)
rb_RSE7 <- sqrt(sum(rbGS_residuals^2) / (length(rbGS_residuals) - length(rb_GS_model$coefficients) - 1))

rb_variable_names <- c("RushingYds_gm", "RushingAtt_gm", "Rec_gm", "Tgt_gm", "ReceivingYds_gm", "RushingTD_gm", "GS")
rb_RSE_values <- c(rb_RSE1, rb_RSE2, rb_RSE3, rb_RSE4, rb_RSE5, rb_RSE6, rb_RSE7)
rb_RSE_table <- data.frame(Variable = rb_variable_names, RSE = rb_RSE_values)
print(rb_RSE_table)
```



```{r}
#WR Linear Models
wr_GS_model <- lm(FantasyPoints_gm ~ GS, data = wr_gm)
wr_Tgt_gm_model <- lm(FantasyPoints_gm ~ Tgt_gm, data = wr_gm)
wr_Rec_gm_model <- lm(FantasyPoints_gm ~ Rec_gm, data = wr_gm)
wr_ReceivingTD_gm_model <- lm(FantasyPoints_gm ~ ReceivingTD_gm, data = wr_gm)
wr_ReceivingYds_gm_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm, data = wr_gm)

# Adjusted R squared values
ReceivingYds_gm_summary <- summary(wr_ReceivingYds_gm_model)
adjusted_r_squared <- ReceivingYds_gm_summary$adj.r.squared
adjusted_r_squared

Rec_gm_summary <- summary(wr_Rec_gm_model)
adjusted_r_squared <- Rec_gm_summary$adj.r.squared
adjusted_r_squared

Tgt_gm_summary <- summary(wr_Tgt_gm_model)
adjusted_r_squared <- Tgt_gm_summary$adj.r.squared
adjusted_r_squared

ReceivingTD_gm_summary <- summary(wr_ReceivingTD_gm_model)
adjusted_r_squared <- ReceivingTD_gm_summary$adj.r.squared
adjusted_r_squared

GS_summary <- summary(wr_GS_model)
adjusted_r_squared <- GS_summary$adj.r.squared
adjusted_r_squared

# Combined WR model
all_wr_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm + Rec_gm + Tgt_gm + ReceivingTD_gm + GS, data = wr_gm)
summary(all_wr_model)

```

WR prediction equation
FantasyPoints_gm = -0.006 + 0.111(ReceivingYds_gm) + 0.562(Rec_gm) + 0.119(Tgt_gm) +  5.687(ReceivingTD_gm) - 0.014(GS)


```{r}
# WR Residual Standard Error
wrRecYds_residuals <- resid(wr_ReceivingYds_gm_model)
wr_RSE1 <- sqrt(sum(wrRecYds_residuals^2) / (length(wrRecYds_residuals) - length(wr_ReceivingYds_gm_model$coefficients) - 1))

wrRec_residuals <- resid(wr_Rec_gm_model)
wr_RSE2 <- sqrt(sum(wrRec_residuals^2) / (length(wrRec_residuals) - length(wr_Rec_gm_model$coefficients) - 1))

wrTgt_residuals <- resid(wr_Tgt_gm_model)
wr_RSE3 <- sqrt(sum(wrTgt_residuals^2) / (length(wrTgt_residuals) - length(wr_Tgt_gm_model$coefficients) - 1))

wrRecTD_residuals <- resid(wr_ReceivingTD_gm_model)
wr_RSE4 <- sqrt(sum(wrRecTD_residuals^2) / (length(wrRecTD_residuals) - length(wr_ReceivingTD_gm_model$coefficients) - 1))

wrGS_residuals <- resid(wr_GS_model)
wr_RSE5 <- sqrt(sum(wrGS_residuals^2) / (length(wrGS_residuals) - length(wr_GS_model$coefficients) - 1))

wr_variable_names <- c("ReceivingYds_gm", "Rec_gm", "Tgt_gm", "ReceivingTD", "GS")
wr_RSE_values <- c(wr_RSE1, wr_RSE2, wr_RSE3, wr_RSE4, wr_RSE5)
wr_RSE_table <- data.frame(Variable = wr_variable_names, RSE = wr_RSE_values)
print(wr_RSE_table)
```



```{r}
#TE Linear Models
te_Tgt_gm_model <- lm(FantasyPoints_gm ~ Tgt_gm, data = te_gm)
te_Rec_gm_model <- lm(FantasyPoints_gm ~ Rec_gm, data = te_gm)
te_ReceivingTD_gm_model <- lm(FantasyPoints_gm ~ ReceivingTD_gm, data = te_gm)
te_ReceivingYds_gm_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm, data = te_gm)

# Adjusted R squared values
ReceivingYds_gm_summary <- summary(te_ReceivingYds_gm_model)
adjusted_r_squared <- ReceivingYds_gm_summary$adj.r.squared
adjusted_r_squared

Rec_gm_summary <- summary(te_Rec_gm_model)
adjusted_r_squared <- Rec_gm_summary$adj.r.squared
adjusted_r_squared

Tgt_gm_summary <- summary(te_Tgt_gm_model)
adjusted_r_squared <- Tgt_gm_summary$adj.r.squared
adjusted_r_squared

ReceivingTD_gm_summary <- summary(te_ReceivingTD_gm_model)
adjusted_r_squared <- ReceivingTD_gm_summary$adj.r.squared
adjusted_r_squared

# Combined TE model
all_te_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm + Rec_gm + Tgt_gm + ReceivingTD_gm, data = te_gm)
summary(all_te_model)

```

TE prediction equation
FantasyPoints_gm = 0.004 + 0.103(ReceivingYds_gm) + 0.552(Rec_gm) + 0.135(Tgt_gm) +  6.03(ReceivingTD_gm)

```{r}
# TE Residual Standard Error
teRecYds_residuals <- resid(te_ReceivingYds_gm_model)
te_RSE1 <- sqrt(sum(teRecYds_residuals^2) / (length(teRecYds_residuals) - length(te_ReceivingYds_gm_model$coefficients) - 1))

teRec_residuals <- resid(te_Rec_gm_model)
te_RSE2 <- sqrt(sum(teRec_residuals^2) / (length(teRec_residuals) - length(te_Rec_gm_model$coefficients) - 1))

teTgt_residuals <- resid(te_Tgt_gm_model)
te_RSE3 <- sqrt(sum(teTgt_residuals^2) / (length(teTgt_residuals) - length(te_Tgt_gm_model$coefficients) - 1))

teRecTD_residuals <- resid(te_ReceivingTD_gm_model)
te_RSE4 <- sqrt(sum(teRecTD_residuals^2) / (length(teRecTD_residuals) - length(te_ReceivingTD_gm_model$coefficients) - 1))

te_variable_names <- c("ReceivingYds_gm", "Rec_gm", "Tgt_gm", "ReceivingTD")
te_RSE_values <- c(te_RSE1, te_RSE2, te_RSE3, te_RSE4)
te_RSE_table <- data.frame(Variable = te_variable_names, RSE = te_RSE_values)
print(te_RSE_table)
```