---
title: "Group Project"
author: "Beau Belkowski, Brian Marquardt"
date: '2024-02-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
#y2021 <- read.csv("2021.csv")
```

```{r}

y2021 <- read.csv("2021.csv")
y2019 <- read.csv("2019.csv")
y2018 <- read.csv("2018.csv")
y2017 <- read.csv("2017.csv")
y2016 <- read.csv("2016.csv")

y2021
y2019
y2018
y2017
y2016
```

```{r}
y2021$G <- as.double(y2021$G)
y2021$GS <- as.double(y2021$GS)
y2021$Age <- as.double(y2021$Age)
y2021
```

```{r}
y2021$year<- rep('2021', times= nrow(y2021))
y2021.1 <- y2021[,-1]
y2021.1
y2018$year<- rep('2018', times= nrow(y2018))
y2018.1 <- y2018[,-1]
y2018.1
y2019$year<- rep('2019', times= nrow(y2019))
y2019.1 <- y2019[,-1]
y2019.1
y2017$year<- rep('2017', times= nrow(y2017))
y2017.1 <- y2017[,-1]
y2017.1
y2016$year<- rep('2016', times= nrow(y2016))
y2016.1 <- y2016[,-1]
y2016.1


fb <- rbind(y2021.1, y2019.1, y2018.1, y2017.1, y2016.1)
fb
```
```{r}
fb$Tgt_gm <- fb$Tgt/fb$G
fb$Rec_gm <- fb$Rec/fb$G
fb$PassingYds_gm <- fb$PassingYds/fb$G
fb$PassingTD_gm <- fb$PassingTD/fb$G
fb$PassingAtt_gm <- fb$PassingAtt/fb$G
fb$RushingYds_gm <- fb$RushingYds/fb$G
fb$RushingTD_gm <- fb$RushingTD/fb$G
fb$RushingAtt_gm <- fb$RushingAtt/fb$G
fb$ReceivingYds_gm <- fb$ReceivingYds/fb$G
fb$ReceivingTD_gm <- fb$ReceivingTD/fb$G
fb$FantasyPoints_gm <- fb$FantasyPoints/fb$G
fb$Int_gm <- fb$Int/fb$G
fb$Fumbles_gm <- fb$Fumbles/fb$G
fb$FumblesLost_gm <- fb$FumblesLost/fb$G
summary(fb)
```

```{r}
library(tidyverse)
rb <- fb %>%
  filter(Pos == "RB")
qb <- fb %>%
  filter(Pos == "QB")
wr <- fb %>%
  filter(Pos == "WR")
te <- fb %>%
  filter(Pos == "TE")
rb
qb
wr
te
```

<<<<<<< Updated upstream
=======

```{r}

rb1 <- rb %>%
  filter(RushingYds_gm == 0)
rb1
```

```{r}
qb_gm <- qb %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

rb_gm <- rb %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

wr_gm <- wr %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)

te_gm <- te %>%
  select(Player, Tm, Pos, Age, G, GS, , year, Tgt_gm, Rec_gm, PassingYds_gm, PassingTD_gm, PassingAtt_gm, RushingYds_gm, RushingTD_gm, RushingAtt_gm, ReceivingYds_gm, ReceivingTD_gm, FantasyPoints_gm, Int_gm, Fumbles_gm, FumblesLost_gm)
```


```{r}
library(corrplot)

qbcorr <- subset(qb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(qbcorr), method ="circle")

rbcorr <- subset(rb_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(rbcorr), method ="circle")

wrcorr <- subset(wr_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(wrcorr), method ="circle")

tecorr <- subset(te_gm, select = -c(Tm, Pos, Player, year))
corrplot(cor(tecorr), method ="circle")
```
```{r}
# Most highly correlated stats with qb success
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingTD_gm)
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingYds_gm)
cor(qb_gm$FantasyPoints_gm, qb_gm$GS)
cor(qb_gm$FantasyPoints_gm, qb_gm$PassingAtt_gm)
```

```{r}
ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(qb_gm, aes(x = FantasyPoints_gm, y = PassingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```


```{r}
# Most highly correlated stats with rb success
cor(rb_gm$FantasyPoints_gm, rb_gm$Tgt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$Rec_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$RushingAtt_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingYds_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$ReceivingTD_gm)
cor(rb_gm$FantasyPoints_gm, rb_gm$GS)
```

```{r}
ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = RushingAtt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(rb_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
# Most highly correlated stats with wr success
cor(wr_gm$FantasyPoints_gm, wr_gm$GS)
cor(wr_gm$FantasyPoints_gm, wr_gm$Tgt_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$Rec_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingTD_gm)
cor(wr_gm$FantasyPoints_gm, wr_gm$ReceivingYds_gm)
```

```{r}
ggplot(wr_gm, aes(x = FantasyPoints_gm, y = GS)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(wr_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
# Most highly correlated stats with te success
cor(te_gm$FantasyPoints_gm, te_gm$Tgt_gm)
cor(te_gm$FantasyPoints_gm, te_gm$Rec_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingTD_gm)
cor(te_gm$FantasyPoints_gm, te_gm$ReceivingYds_gm)
```

```{r}
library(ggplot2)
ggplot(te_gm, aes(x = FantasyPoints_gm, y = Tgt_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = Rec_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingTD_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)

ggplot(te_gm, aes(x = FantasyPoints_gm, y = ReceivingYds_gm)) + 
  geom_point()+ 
  geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```

```{r}
#QB Linear Models
qb_PassingTD_gm_model <- lm(FantasyPoints_gm ~ PassingTD_gm, data = qb_gm)
qb_PassingYds_gm_model <- lm(FantasyPoints_gm ~ PassingYds_gm, data = qb_gm)
qb_GS_model <- lm(FantasyPoints_gm ~ GS, data = qb_gm)
qb_PassingAtt_gm_model <- lm(FantasyPoints_gm ~ PassingAtt_gm, data = qb_gm)

# Adjusted R squared values
PassingTD_summary <- summary(qb_PassingTD_gm_model)
adjusted_r_squared <- PassingTD_summary$adj.r.squared
adjusted_r_squared

PassingYds_summary <- summary(qb_PassingYds_gm_model)
adjusted_r_squared <- PassingYds_summary$adj.r.squared
adjusted_r_squared

PassingAtt_summary <- summary(qb_PassingAtt_gm_model)
adjusted_r_squared <- PassingAtt_summary$adj.r.squared
adjusted_r_squared

GS_summary <- summary(qb_GS_model)
adjusted_r_squared <- GS_summary$adj.r.squared
adjusted_r_squared


# Combined QB model
all_qb_model <- lm(FantasyPoints_gm ~ PassingTD_gm + PassingYds_gm + PassingAtt_gm + GS, data = qb_gm)
summary(all_qb_model)


```
QB prediction equation
FantasyPoints_gm = 0.361 + 4.335(PassingTD_gm) + 0.034(PassingYds_gm) - 0.031(PassingAtt_gm) + 0.153(GS)


```{r}
# QB Residual Standard Error
qbTD_residuals <- resid(qb_PassingTD_gm_model)
qb_RSE1 <- sqrt(sum(qbTD_residuals^2) / (length(qbTD_residuals) - length(qb_PassingTD_gm_model$coefficients) - 1))

qbYds_residuals <- resid(qb_PassingYds_gm_model)
qb_RSE2 <- sqrt(sum(qbYDS_residuals^2) / (length(qbYDS_residuals) - length(qb_PassingYds_gm_model$coefficients) - 1))

qbGS_residuals <- resid(qb_GS_model)
qb_RSE3 <- sqrt(sum(qbGS_residuals^2) / (length(qbGS_residuals) - length(qb_GS_model$coefficients) - 1))

qbAtt_residuals <- resid(qb_PassingAtt_gm_model)
qb_RSE4 <- sqrt(sum(qbAtt_residuals^2) / (length(qbAtt_residuals) - length(qb_PassingAtt_gm_model$coefficients) - 1))

qb_variable_names <- c("PassingTD_gm", "PassingYds_gm", "PassingAtt_gm", "GS")
qb_RSE_values <- c(qb_RSE1, qb_RSE2, qb_RSE3, qb_RSE4)
qb_RSE_table <- data.frame(Variable = qb_variable_names, RSE = qb_RSE_values)
print(qb_RSE_table)
```




```{r}
#RB Linear Models
rb_Tgt_gm_model <- lm(FantasyPoints_gm ~ Tgt_gm, data = rb_gm)
rb_Rec_gm_model <- lm(FantasyPoints_gm ~ Rec_gm, data = rb_gm)
rb_RushingYds_gm_model <- lm(FantasyPoints_gm ~ RushingYds_gm, data = rb_gm)
rb_RushingTD_gm_model <- lm(FantasyPoints_gm ~ RushingTD_gm, data = rb_gm)
rb_RushingAtt_gm_model <- lm(FantasyPoints_gm ~ RushingAtt_gm, data = rb_gm)
rb_ReceivingYds_gm_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm, data = rb_gm)
rb_ReceivingTD_gm_model <- lm(FantasyPoints_gm ~ ReceivingTD_gm, data = rb_gm)
rb_GS_model <- lm(FantasyPoints_gm ~ GS, data = rb_gm)


# Adjusted R squared values
RushingYds_gm_summary <- summary(rb_RushingYds_gm_model)
adjusted_r_squared <- RushingYds_gm_summary$adj.r.squared
adjusted_r_squared

RushingAtt_gm_summary <- summary(rb_RushingAtt_gm_model)
adjusted_r_squared <- RushingAtt_gm_summary$adj.r.squared
adjusted_r_squared

Rec_gm_summary <- summary(rb_Rec_gm_model)
adjusted_r_squared <- Rec_gm_summary$adj.r.squared
adjusted_r_squared

Tgt_gm_summary <- summary(rb_Tgt_gm_model)
adjusted_r_squared <- Tgt_gm_summary$adj.r.squared
adjusted_r_squared

ReceivingYds_gm_summary <- summary(rb_ReceivingYds_gm_model)
adjusted_r_squared <- ReceivingYds_gm_summary$adj.r.squared
adjusted_r_squared

RushingTD_gm_summary <- summary(rb_RushingTD_gm_model)
adjusted_r_squared <- RushingTD_gm_summary$adj.r.squared
adjusted_r_squared

GS_summary <- summary(rb_GS_model)
adjusted_r_squared <- GS_summary$adj.r.squared
adjusted_r_squared

ReceivingTD_gm_summary <- summary(rb_ReceivingTD_gm_model)
adjusted_r_squared <- ReceivingTD_gm_summary$adj.r.squared
adjusted_r_squared

# Combined RB model
all_rb_model <- lm(FantasyPoints_gm ~ Tgt_gm + Rec_gm + RushingYds_gm + RushingTD_gm + RushingAtt_gm + ReceivingYds_gm + ReceivingTD_gm + GS, data = rb_gm)
summary(all_rb_model)

```
RB prediction equation
FantasyPoints_gm = -0.059 + 0.286(Tgt_gm) + 0.347(Rec_gm) - 0.101(RushingYds_gm) + 5.972(RushingTD_gm) - 0.018(RushingAtt_gm) + 0.115(ReceivingYds_gm) + 6.253(ReceivingTD_gm) - 0.005(GS)

```{r}
# RB Residual Standard Error
rbRushYds_residuals <- resid(rb_RushingYds_gm_model)
rb_RSE1 <- sqrt(sum(rbRushYds_residuals^2) / (length(rbRushYds_residuals) - length(rb_RushingYds_gm_model$coefficients) - 1))

rbRushAtt_residuals <- resid(rb_RushingAtt_gm_model)
rb_RSE2 <- sqrt(sum(rbRushAtt_residuals^2) / (length(rbRushAtt_residuals) - length(rb_RushingAtt_gm_model$coefficients) - 1))

rbRec_residuals <- resid(rb_Rec_gm_model)
rb_RSE3 <- sqrt(sum(rbRec_residuals^2) / (length(rbRec_residuals) - length(rb_Rec_gm_model$coefficients) - 1))

rbTgt_residuals <- resid(rb_Tgt_gm_model)
rb_RSE4 <- sqrt(sum(rbTgt_residuals^2) / (length(rbTgt_residuals) - length(rb_Tgt_gm_model$coefficients) - 1))

rbRecYds_residuals <- resid(rb_ReceivingYds_gm_model)
rb_RSE5 <- sqrt(sum(rbRecYds_residuals^2) / (length(rbRecYds_residuals) - length(rb_ReceivingYds_gm_model$coefficients) - 1))

rbRushTD_residuals <- resid(rb_RushingTD_gm_model)
rb_RSE6 <- sqrt(sum(rbRushTD_residuals^2) / (length(rbRushTD_residuals) - length(rb_RushingTD_gm_model$coefficients) - 1))

rbGS_residuals <- resid(rb_GS_model)
rb_RSE7 <- sqrt(sum(rbGS_residuals^2) / (length(rbGS_residuals) - length(rb_GS_model$coefficients) - 1))

rb_variable_names <- c("RushingYds_gm", "RushingAtt_gm", "Rec_gm", "Tgt_gm", "ReceivingYds_gm", "RushingTD_gm", "GS")
rb_RSE_values <- c(rb_RSE1, rb_RSE2, rb_RSE3, rb_RSE4, rb_RSE5, rb_RSE6, rb_RSE7)
rb_RSE_table <- data.frame(Variable = rb_variable_names, RSE = rb_RSE_values)
print(rb_RSE_table)
```



```{r}
#WR Linear Models
wr_GS_model <- lm(FantasyPoints_gm ~ GS, data = wr_gm)
wr_Tgt_gm_model <- lm(FantasyPoints_gm ~ Tgt_gm, data = wr_gm)
wr_Rec_gm_model <- lm(FantasyPoints_gm ~ Rec_gm, data = wr_gm)
wr_ReceivingTD_gm_model <- lm(FantasyPoints_gm ~ ReceivingTD_gm, data = wr_gm)
wr_ReceivingYds_gm_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm, data = wr_gm)

# Adjusted R squared values
ReceivingYds_gm_summary <- summary(wr_ReceivingYds_gm_model)
adjusted_r_squared <- ReceivingYds_gm_summary$adj.r.squared
adjusted_r_squared

Rec_gm_summary <- summary(wr_Rec_gm_model)
adjusted_r_squared <- Rec_gm_summary$adj.r.squared
adjusted_r_squared

Tgt_gm_summary <- summary(wr_Tgt_gm_model)
adjusted_r_squared <- Tgt_gm_summary$adj.r.squared
adjusted_r_squared

ReceivingTD_gm_summary <- summary(wr_ReceivingTD_gm_model)
adjusted_r_squared <- ReceivingTD_gm_summary$adj.r.squared
adjusted_r_squared

GS_summary <- summary(wr_GS_model)
adjusted_r_squared <- GS_summary$adj.r.squared
adjusted_r_squared

# Combined WR model
all_wr_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm + Rec_gm + Tgt_gm + ReceivingTD_gm + GS, data = wr_gm)
summary(all_wr_model)

```

WR prediction equation
FantasyPoints_gm = -0.006 + 0.111(ReceivingYds_gm) + 0.562(Rec_gm) + 0.119(Tgt_gm) +  5.687(ReceivingTD_gm) - 0.014(GS)


```{r}
# WR Residual Standard Error
wrRecYds_residuals <- resid(wr_ReceivingYds_gm_model)
wr_RSE1 <- sqrt(sum(wrRecYds_residuals^2) / (length(wrRecYds_residuals) - length(wr_ReceivingYds_gm_model$coefficients) - 1))

wrRec_residuals <- resid(wr_Rec_gm_model)
wr_RSE2 <- sqrt(sum(wrRec_residuals^2) / (length(wrRec_residuals) - length(wr_Rec_gm_model$coefficients) - 1))

wrTgt_residuals <- resid(wr_Tgt_gm_model)
wr_RSE3 <- sqrt(sum(wrTgt_residuals^2) / (length(wrTgt_residuals) - length(wr_Tgt_gm_model$coefficients) - 1))

wrRecTD_residuals <- resid(wr_ReceivingTD_gm_model)
wr_RSE4 <- sqrt(sum(wrRecTD_residuals^2) / (length(wrRecTD_residuals) - length(wr_ReceivingTD_gm_model$coefficients) - 1))

wrGS_residuals <- resid(wr_GS_model)
wr_RSE5 <- sqrt(sum(wrGS_residuals^2) / (length(wrGS_residuals) - length(wr_GS_model$coefficients) - 1))

wr_variable_names <- c("ReceivingYds_gm", "Rec_gm", "Tgt_gm", "ReceivingTD", "GS")
wr_RSE_values <- c(wr_RSE1, wr_RSE2, wr_RSE3, wr_RSE4, wr_RSE5)
wr_RSE_table <- data.frame(Variable = wr_variable_names, RSE = wr_RSE_values)
print(wr_RSE_table)
```



```{r}
#TE Linear Models
te_Tgt_gm_model <- lm(FantasyPoints_gm ~ Tgt_gm, data = te_gm)
te_Rec_gm_model <- lm(FantasyPoints_gm ~ Rec_gm, data = te_gm)
te_ReceivingTD_gm_model <- lm(FantasyPoints_gm ~ ReceivingTD_gm, data = te_gm)
te_ReceivingYds_gm_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm, data = te_gm)

# Adjusted R squared values
ReceivingYds_gm_summary <- summary(te_ReceivingYds_gm_model)
adjusted_r_squared <- ReceivingYds_gm_summary$adj.r.squared
adjusted_r_squared

Rec_gm_summary <- summary(te_Rec_gm_model)
adjusted_r_squared <- Rec_gm_summary$adj.r.squared
adjusted_r_squared

Tgt_gm_summary <- summary(te_Tgt_gm_model)
adjusted_r_squared <- Tgt_gm_summary$adj.r.squared
adjusted_r_squared

ReceivingTD_gm_summary <- summary(te_ReceivingTD_gm_model)
adjusted_r_squared <- ReceivingTD_gm_summary$adj.r.squared
adjusted_r_squared

# Combined TE model
all_te_model <- lm(FantasyPoints_gm ~ ReceivingYds_gm + Rec_gm + Tgt_gm + ReceivingTD_gm, data = te_gm)
summary(all_te_model)

```

TE prediction equation
FantasyPoints_gm = 0.004 + 0.103(ReceivingYds_gm) + 0.552(Rec_gm) + 0.135(Tgt_gm) +  6.03(ReceivingTD_gm)

```{r}
# TE Residual Standard Error
teRecYds_residuals <- resid(te_ReceivingYds_gm_model)
te_RSE1 <- sqrt(sum(teRecYds_residuals^2) / (length(teRecYds_residuals) - length(te_ReceivingYds_gm_model$coefficients) - 1))

teRec_residuals <- resid(te_Rec_gm_model)
te_RSE2 <- sqrt(sum(teRec_residuals^2) / (length(teRec_residuals) - length(te_Rec_gm_model$coefficients) - 1))

teTgt_residuals <- resid(te_Tgt_gm_model)
te_RSE3 <- sqrt(sum(teTgt_residuals^2) / (length(teTgt_residuals) - length(te_Tgt_gm_model$coefficients) - 1))

teRecTD_residuals <- resid(te_ReceivingTD_gm_model)
te_RSE4 <- sqrt(sum(teRecTD_residuals^2) / (length(teRecTD_residuals) - length(te_ReceivingTD_gm_model$coefficients) - 1))

te_variable_names <- c("ReceivingYds_gm", "Rec_gm", "Tgt_gm", "ReceivingTD")
te_RSE_values <- c(te_RSE1, te_RSE2, te_RSE3, te_RSE4)
te_RSE_table <- data.frame(Variable = te_variable_names, RSE = te_RSE_values)
print(te_RSE_table)
```


>>>>>>> Stashed changes
